SoK: The Evolution of Defenses Against Web Application Attacks

### 2014-10-29 docs/questioning.tex
started parse-tree validation

\begin{figure*}
\begin{center}
\leavevmode
\includegraphics[scale=0.57]{attacks-steps.pdf}
\end{center}
\caption{\label{fig:attacks}Attack model demonstrating web
application attacks based on executable source
code injection vulnerabilities. For every arrow there is a
corresponding tuple that includes the step number for
every attack. Note that {\sc xss} attacks can also involve
{\it phishing}. Every {\it locus} indicates a step where mechanisms
detect attacks. For every locus we provide the corresponding
references: ({\sc draft}).}
\end{figure*}

@@

The mechanism based on this method compare the parse tree of a
query before the inclusion of user input with the one resulting after
the inclusion of user input. If the trees diverge, the application
is probably under attack.

@@

\subsubsection{Instruction Set Randomization --- ISR}

>>>>

\begin{figure*}
\begin{center}
\leavevmode
\includegraphics[scale=0.61]{attacks-steps.pdf}
\end{center}
\caption{\label{fig:attacks}Attack model demonstrating web
application attacks based on executable source
code injection vulnerabilities. For every arrow there is a
corresponding tuple that includes the step number for
every attack. Note that {\sc xss} attacks can also involve
{\it phishing}. Every {\it locus} indicates a step where mechanisms
detect attacks. For every locus we provide the corresponding
references: ({\sc draft}).}
\end{figure*}

@@

The key idea behind this approach, is to compare
the tree representation of the abstract syntactic
structure of the executable source code that is
about to be executed with the one hat was originally intended.
If the trees diverge, the application is probably under attack.

In the case of {\sc dsl} injection attacks, mechanisms check 
the query before the inclusion of user input with the one
resulting after the inclusion of user input.

@@

\subsubsection{Instruction Set Randomization (ISR)}
